%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper, 10pt]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage[normalem]{ulem}
\usepackage{color}
\usepackage{tikz}
\usepackage{hyperref}
\renewcommand{\familydefault}{\rmdefault}
\begin{document}



%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection {\bf Abhirup}{\bf Das} % Your name
{{\hspace{10pt}}{\href{https://www.linkedin.com/in/abhirup-das-46462463/}{https://www.linkedin.com/in/abhirup-das-46462463/}}\\ {{\hspace{10pt}}abhirup.das@hotmail.com | 647-972-3732}}\\
%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\fbox{\begin{minipage}[t]{0.30\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Education
%------------------------------------------------


\color{blue}
\sectionspace
\section{Education}



\subsection{University of Waterloo}


\descript{B.A.S Computer Engineering}
\textnormal{\textbf{2015-2021}}\\

%subsection{Co-op Duration}
%\textnormal\textbf{8 months preferred}\\

%------------------------------------------------


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}
\sectionspace
\subsection{Languages}
\textbullet{} C (industry knowledge) \\ 
\textbullet{} C++ (academic knowledge only) \\
\textbullet{} Python (adept)\\ 
\textbullet{} x86 ASM (basic knowledge) \\
\textbullet{} aarch64 ASM (basic knowledge) \\

\sectionspace
\sectionspace

\subsection{Platforms}
\textbullet{} QNX (kernel internals \& libc \\
\hspace{2.5mm} knowledge) \\
\textbullet{} Linux (kernel \& user space \\
\hspace{2.5mm} knowledge) \\
\textbullet{} NetBSD (kernel space \\
\hspace{2.5mm} knowledge) \\
\textbullet{} FreeBSD \\
\sectionspace % Some whitespace after the section
\sectionspace
\subsection{Software Tools}
\textbullet{} GCC (assembly inlining, built-ins \\
\hspace{2.5mm} \& attributes) \\ 
\textbullet{} GDB (introductory knowledge)\\
\textbullet{} GNU Make \\
\textbullet{} Valgrind 

\sectionspace % Some whitespace after the section
\sectionspace
\subsection{Hardware Protocols}

\textbullet{} I2C \textbullet{} UART \textbullet{} SPI \\
\textbullet{} Bluetooth Low Energy \\ 
\hspace{2.5mm} (introductory knowledge) \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}
\subsection{HW/SW related}
\textbullet{} Operating Systems \\
\textbullet{} Data Structures and Algorithms \\
\textbullet{} Digital Computers \\
\textbullet{} Electronic Circuits 1\\
\sectionspace % Some whitespace after the section

\sectionspace
\sectionspace
\sectionspace
\end{minipage}} \hspace{.5cm}% The end of the left column
%\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.65\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\vspace{1mm} \section{Work Experience}

\runsubsection{Core OS SW Developer}
\descript{| QNX Software Systems}
\location{September 2017 – December 2017 \hspace{1mm}| Ottawa, Canada}
\textit{\bf{C,GDB, GCC, x86 \& aarch64 assembly, Makefiles}}
%{\it Bluetooth Low Energy, C, Assembly, I2C, UART, Python}
\vspace{\topsep}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
%\item Worked with a multi-core system for a hearing aid device
\item Learned domain specific knowledge about the virtual memory manager, dynamic loader, malloc implementation, Makefile build system and the ext3 file system.
\item Gained a deep understanding of kernel internals, kernel development, testing process, ARM and x86 based hardware architectures. 
\item Developed unit tests for QNX's implementation of lib/c and core kernel components, including memory manager, process manager and profiler tool. 
\item Read through architecture specific assembly and C source code, to develop unit tests resulting in functional and 100\% code coverage.
\item Debugged unit tests on ARM32 and aarch64 qemu environments on Linux using GDB.
\end{tightitemize}
\sectionspace 

\runsubsection{Hardware \& Software Developer}
\descript{| ON Semiconductor}
\location{May 2017 – August 2017 \hspace{1mm}| Waterloo, Canada}
\textit{\bf{BLE (Bluetooth Low Energy), C, GDB, JTAG}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed BLE and power firmware samples for ARM Cortex-M3 BLE SoC, in an agile work environment.
\item Created a new power initialization sample that wrote power values and initialization instructions into non-volatile region of memory.
\item Used GDB \& JTAG interface to probe Cortex-M3's physical memory space for validation and hardware fault detection.
\item Learned to comb through hardware specific reference manuals to bring up and debug bare metal software. 
%\item Successfully developed and applied alternative algorithms to create a test case in order to bypass a web application bug
\end{tightitemize}

\sectionspace
\runsubsection{Graphics Software Developer}
\descript{| QNX Software Systems}
\location{September 2016 – December 2016 \hspace{1mm}| Ottawa, Canada}
\textit{\bf{OpenGL, C, GDB}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed font rendering test application for QNX RTOS, using OpenGL and Font FreeType library. 
\item Used GDB to cross debug application on j6 ARM32 development board.
\item Gained a good understanding of the graphics pipeline and the use of the OpenGL library. 
\end{tightitemize}
\sectionspace

\runsubsection{Embedded Software Developer}
\descript{| University of Waterloo Real time Embedded Systems Lab}
\location{May 2015 – December 2015 \hspace{1mm}| Waterloo, Canada}
\textit{\bf{Gentoo Linux, Network Driver debugging, Python, BASH}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Completed the hardware bring up of Intel's Galileo development board using Gentoo Linux. 
\item Investigated and troubleshot Gentoo Linux issues, from installation to missing network drivers.
\item Cross compiled and tested several versions of the Linux kernel with separate drivers to successfully enable networking on the board. 
\end{tightitemize}
\sectionspace

\end{minipage} % The end of the right column


\end{document}
